Mapping Cancer: the Potential of Cartograms and Alternative Map Displays

### 2020-05-22 letter2/submission2.Rmd
letter to reviewers

---
from: Stephanie Kobakian
fromqualifications: B.Com and B.Eco
fromemail: stephanie.kobakian@monash.edu
fromphone: +61 433 699 797
fromsignature: sigfile.png
toname: Professor Peter Baade and Dr Susanna Cramb
opening: Dear Professor Peter Baade and Dr Susanna Cramb,
closing: Warm regards
spacing: 1.4
output: MonashEBSTemplates::letter
---

@@

This study summarises current practices for cancer atlases and investigates the alternative map displays that could be used to accurately represent the distribution of cancer statistics across a population, as many cancer atlases lack appropriate displays for population statistics.

@@

XXX

>>>>

---
from: Stephanie Kobakian
fromqualifications: B.Com and B.Eco
fromemail: stephanie.kobakian@monash.edu
fromphone: +61 433 699 797
fromsignature: sigfile.png
toname: Professor Peter Baade and Dr Susanna Cramb
opening: Dear Professor Peter and Dr Susanna,
closing: Warm regards
spacing: 1.4
output: MonashEBSTemplates::letter
---

@@

*This study summarises current practices for cancer atlases and investigates the alternative map displays that could be used to accurately represent the distribution of cancer statistics across a population, as many cancer atlases lack appropriate displays for population statistics.*

@@

### 2020-05-22 literature.Rmd
letter to reviewers

| Fig. | Atlas | Data | Statistic | Source |
|------|------------|-----------|----------------------|-----------------------------|
| a | The Environment and Health<br> Atlas of England and Wales<br> [@EnvEnglandWales2] | Sex: Women<br> Year: 2010<br> Cancer: Lung | Relative risk | [Office for National Statistics<br> (ONS) (England) and from the<br> Welsh Cancer Intelligence and<br> Surveillance Unit (WCISU)](http://www.envhealthatlas.co.uk/homepage/) |
| b | Globocan 2018: Estimated Cancer<br> Incidence, Mortality and <br> <br> prevalence Worldwide<br> [@Globocan] | Sex: Both<br> Year: 2018<br> Cancer: All invasive | Age standardized<br> incidence rates<br> (per 100,000) | [World Health Organization's<br> International Agency for<br> Research on Cancer](https://www.iarc.fr/<br>  |
| c | Atlas of Cancer in Queensland<br>  [@QLDcancerAtlas] | Sex: Males<br> Year: 1998 - 2007<br> Cancer: Lung | Relative incidence<br> ratio | [Queensland Cancer Registry](https://cancerqld.org.au/research/cancer-registries/queensland-cancer-registry/) |
| d | Australian Cancer Atlas<br> [@ACA] | Sex: Males<br> Year: 2010 - 2014<br> Cancer: Lung | Average standardised<br> incidence rate | [Australian Cancer Atlas](https://atlas.cancer.org.au/) |
| e | United States Cancer<br> Statistics: An Interactive<br> Cancer Statistics Website<br>  | Sex: Both<br> Year: 2016<br> Cancer: All types | Incidence rate per<br> 100,000 | With data from state cancer<br> registries: <br> [Centers for Disease Control and Prevention](https://www.cdc.gov/) |
| f | Map of Cancer Mortality<br> Rates in Spain<br> [@cancerSpain] | Sex: Both<br> Year: 2004 - 2008<br> Cancer: All types | Relative risk | <br> [Map of cancer mortality rates<br> in Spain](https://elpais.com/elpais/2014/10/06/media/1412612722_141933.html |
| g | Atlas of Childhood<br> Cancer in Ontario<br> [@OntarioPediatric] | Sex: Both<br> Year: 1995 - 2004<br> Cancer: All types | Incidence rate per<br> 100,00 | <br> [The Pediatric Oncology Group<br> of Ontario Networked Information<br> System](https://www.pogo.ca/research-data/pogonis-childhood-cancer-database/data-requests/) |

>>>>

| Fig. | Atlas | Data | Statistic | Source |
|------|------------|-----------|----------------------|------------------|
| a | The Environment and Health<br> Atlas of England and Wales<br> [@EnvEnglandWales2] | Sex: Women<br> Year: 2010<br> Cancer: Lung | Relative risk | [Office for National Statistics<br> (ONS) (England) and from the<br> Welsh Cancer Intelligence and<br> Surveillance Unit (WCISU)](http://www.envhealthatlas.co.uk/homepage/) |
| b | Globocan 2018: Estimated Cancer<br> Incidence, Mortality and <br> <br> prevalence Worldwide<br> [@Globocan] | Sex: Both<br> Year: 2018<br> Cancer: All invasive | Age standardized<br> incidence rates<br> (per 100,000) | [World Health Organization's<br> International Agency for<br> Research on Cancer](https://www.iarc.fr/<br>  |
| c | Atlas of Cancer in Queensland<br>  [@QLDcancerAtlas] | Sex: Males<br> Year: 1998 - 2007<br> Cancer: Lung | Relative incidence<br> ratio | [Queensland Cancer Registry](https://cancerqld.org.au/research/cancer-registries/queensland-cancer-registry/) |
| d | Australian Cancer Atlas<br> [@ACA] | Sex: Males<br> Year: 2010 - 2014<br> Cancer: Lung | Average standardised<br> incidence rate | [Australian Cancer Atlas](https://atlas.cancer.org.au/) |
| e | United States Cancer<br> Statistics: An Interactive<br> Cancer Statistics Website<br>  | Sex: Both<br> Year: 2016<br> Cancer: All types | Incidence rate per<br> 100,000 | With data from state cancer<br> registries: <br> [Centers for Disease Control and Prevention](https://www.cdc.gov/) |
| f | Map of Cancer Mortality<br> Rates in Spain<br> [@cancerSpain] | Sex: Both<br> Year: 2004 - 2008<br> Cancer: All types | Relative risk | <br> [Map of cancer mortality rates<br> in Spain](https://elpais.com/elpais/2014/10/06/media/1412612722_141933.html |
| g | Atlas of Childhood<br> Cancer in Ontario<br> [@OntarioPediatric] | Sex: Both<br> Year: 1995 - 2004<br> Cancer: All types | Incidence rate per<br> 100,00 | <br> [The Pediatric Oncology Group<br> of Ontario Networked Information<br> System](https://www.pogo.ca/research-data/pogonis-childhood-cancer-database/data-requests/) |
